Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-05-08 main.Rmd
non-negative integers, not positive integers

\begin{definition}\label{def:index set}
There is a unique {\bf index set}, $Z=\{z: z \in \mathbb{Z}_{\geq 0}\}$, which map the time instants to a set of positive integers. Often, this is thought of as $t=0, \dots, T$.
\end{definition}

@@

# Hierarchy and ordering {#sec:cyclic-calendar}

>>>>

\begin{definition}\label{def:index set}
There is a unique {\bf index set}, $Z=\{z: z \in \mathbb{Z}_{\geq 0}\}$, which map the time instants to a set of non-negative integers. Often, this is thought of as $t=0, \dots, T$.
\end{definition}

@@

# Relativities {#sec:cyclic-calendar}
